Usability of Mobile Map Applications

### 2014-09-25 usability-study/usability-study.tex
add graphic for heuristic eval

\end{multicols}
\clearpage
\begin{multicols}{2}
[
\subsection{Apple Maps}
]
\par
\noindent
\includegraphics[width=.5\textwidth]{apple-maps.png}
\par
\noindent
One idea that is emphasized in the \textit{iOS Human Interface Guidelines} is to always "defer to content".\cite{Apple} One way in which the guidelines recommend doing this is by taking advantage of the whole screen, which the Apple Maps mobile app seems to be doing. The UI helps people understand and interact with the content, but never competes with it. Reconsider visual indicators of physicality and realism. Bezels, gradients, and drop shadows sometimes lead to heavier UI elements that can overpower or compete with the content. Instead, focus on the content and let the UI play a supporting role.

\end{multicols}
\clearpage
\section{Conclusion}
The usability metrics of the Google Maps mobile application outranked those of the Apple Maps application in almost every way. Though there are some problems with the UI consistency, it does not seem to bother the users (refer back to satisfaction). Still, using non-standard icons or processes isn't without drawbacks. It's loud. It's authorial voice. It's greater cognitive load for users. Anything inconsistent, first or third party is. On an integrated platform like iOS, integrating with the platform offers a lot of benefits, especially when it comes to user experience.

>>>>

\end{multicols}
\clearpage
\begin{multicols}{2}
[
\subsection{Apple Maps}
]
\par
\noindent
\includegraphics[width=.5\textwidth]{apple-maps.png}
\par
\noindent
One guideline from iOS HIG is that important content or functionality should be `elevated':\cite{Apple}
\includegraphics[width=.35\textwidth]{apple-importance.png}
\par
\noindent
This suggests that the icon on the top left-hand corner, which takes you to the directions screen in this case, is the most important. I would have to agree that getting directions is very important functionality, so it seems as if the app is complying to the guidelines. However, a couple of test subjects tried to click on the icon second from the right on the bottom for directions. It is possible that this guideline of important functionality being `elevated' is not intuitive to all users.
\end{multicols}
\medskip
\medskip
\par
The lack of standard iOS icons in the Google Maps app may or may not explain some of the efficiency issues as well as some errors that occurred with the tasks on the mobile Google Maps app. The guideline of important functionality being towards the upper-left corner of the screen may or may not explain some of the efficiency issues as well as errors that occurred with the tasks on the mobile Apple Maps app.
\clearpage
\section{Conclusion}
The usability metrics of the Google Maps mobile application outranked those of the Apple Maps application in almost every way. Though there are some problems with the UI consistency, it does not seem to bother the users (refer back to satisfaction). Still, using non-standard icons or processes isn't without drawbacks. It's loud. It's authorial voice. It's greater cognitive load for users. Anything inconsistent, first or third party is. On an integrated platform like iOS, integrating with the platform offers a lot of benefits, especially when it comes to user experience.
